Differential expression analysis: A pipeline to analyse time-course gene expression data

### 2019-02-28 scripts/02_differential_expression_analysis.Rmd
FIX renamed some functions

# Define contrast	
contrasts = c("M.0-VL.0",
	      "M.3-VL.3",
	      "M.6-VL.6",
	      "M.9-VL.9",
	      "M.12-VL.12",
	      "M.18-VL.18",
	      "M.24-VL.24",
	      "M.30-VL.30",
	      "M.36-VL.36",
	      "M.48-VL.48",
	      "M.60-VL.60",
	      "M.72-VL.72",
	      "M.120-VL.120",
	      "M.168-VL.168")
weekly_de_analysis =  moanin::fit_weekly_analysis(
     data, meta, contrasts,
     use_voom_weights=FALSE)
```

```{r echo=FALSE, results="hide"}
# Run the DE analysis on the rest of the influenza strain.
contrasts = c("M.0-K.0",
	      "M.3-K.3",
	      "M.6-K.6",
	      "M.9-K.9",
	      "M.12-K.12",
	      "M.18-K.18",
	      "M.24-K.24",
	      "M.30-K.30",
	      "M.36-K.36",
	      "M.48-K.48",
	      "M.60-K.60",
	      "M.72-K.72",
	      "M.120-K.120",
	      "M.168-K.168")
K_weekly_de_analysis =  moanin::fit_weekly_analysis(
     data, meta, contrasts,
     use_voom_weights=FALSE)
contrasts = c("M.0-C.0",
	      "M.3-C.3",
	      "M.6-C.6",
	      "M.9-C.9",
	      "M.12-C.12",
	      "M.18-C.18",
	      "M.24-C.24",
	      "M.30-C.30",
	      "M.36-K.36",
	      "M.48-C.48",
	      "M.60-C.60",
	      "M.72-C.72",
	      "M.120-C.120",
	      "M.168-C.168")
C_weekly_de_analysis =  moanin::fit_weekly_analysis(
     data, meta, contrasts,
     use_voom_weights=FALSE)
contrasts = c("M.0-VH.0",
	      "M.3-VH.3",
	      "M.6-VH.6",
	      "M.9-VH.9",
	      "M.12-VH.12",
	      "M.18-VH.18",
	      "M.24-VH.24",
	      "M.30-VH.30",
	      "M.36-VH.36",
	      "M.48-VH.48",
	      "M.60-VH.60",
	      "M.72-VH.72",
	      "M.120-VH.120",
	      "M.168-VH.168")
VH_weekly_de_analysis =  moanin::fit_weekly_analysis(
     data, meta, contrasts,
     use_voom_weights=FALSE)
```

@@

```{r de_analysis}
# Define contrast
de_analysis = data.frame(row.names=row.names(data))
for(contrast_formula in timecourse_contrasts){
    contrast = limma::makeContrasts(
	contrast_formula,
	levels=levels(meta$Group))
    model = moanin:::edgeWithContrasts(as.matrix(data), meta, contrast)
    contrast_name = gsub(" ", "", contrast_formula, fixed=TRUE)
    contrast_name_pval = paste(contrast_name, "-pval", sep="")
    contrast_name_qval = paste(contrast_name, "-qval", sep="")
    de_analysis[contrast_name_pval] = model$pval_lrt
    de_analysis[contrast_name_qval] = model$qval_lrt

>>>>

# Define contrast	
contrasts = c("M.0-VL.0",
	      "M.3-VL.3",
	      "M.6-VL.6",
	      "M.9-VL.9",
	      "M.12-VL.12",
	      "M.18-VL.18",
	      "M.24-VL.24",
	      "M.30-VL.30",
	      "M.36-VL.36",
	      "M.48-VL.48",
	      "M.60-VL.60",
	      "M.72-VL.72",
	      "M.120-VL.120",
	      "M.168-VL.168")
weekly_de_analysis =  moanin::weekly_differential_expression_analysis(
     data, meta, contrasts,
     use_voom_weights=FALSE)
```

```{r echo=FALSE, results="hide"}
# Run the DE analysis on the rest of the influenza strain.
contrasts = c("M.0-K.0",
	      "M.3-K.3",
	      "M.6-K.6",
	      "M.9-K.9",
	      "M.12-K.12",
	      "M.18-K.18",
	      "M.24-K.24",
	      "M.30-K.30",
	      "M.36-K.36",
	      "M.48-K.48",
	      "M.60-K.60",
	      "M.72-K.72",
	      "M.120-K.120",
	      "M.168-K.168")
K_weekly_de_analysis =  moanin::weekly_differential_expression_analysis(
     data, meta, contrasts,
     use_voom_weights=FALSE)
contrasts = c("M.0-C.0",
	      "M.3-C.3",
	      "M.6-C.6",
	      "M.9-C.9",
	      "M.12-C.12",
	      "M.18-C.18",
	      "M.24-C.24",
	      "M.30-C.30",
	      "M.36-K.36",
	      "M.48-C.48",
	      "M.60-C.60",
	      "M.72-C.72",
	      "M.120-C.120",
	      "M.168-C.168")
C_weekly_de_analysis =  moanin::weekly_differential_expression_analysis(
     data, meta, contrasts,
     use_voom_weights=FALSE)
contrasts = c("M.0-VH.0",
	      "M.3-VH.3",
	      "M.6-VH.6",
	      "M.9-VH.9",
	      "M.12-VH.12",
	      "M.18-VH.18",
	      "M.24-VH.24",
	      "M.30-VH.30",
	      "M.36-VH.36",
	      "M.48-VH.48",
	      "M.60-VH.60",
	      "M.72-VH.72",
	      "M.120-VH.120",
	      "M.168-VH.168")
VH_weekly_de_analysis =  moanin::weekly_differential_expression_analysis(
     data, meta, contrasts,
     use_voom_weights=FALSE)
```

@@

```{r de_analysis}
# Define contrast
de_analysis = data.frame(row.names=row.names(data))
for(contrast_formula in timecourse_contrasts){
    contrast = limma::makeContrasts(
	contrasts=contrast_formula,
	levels=levels(meta$Group))
    model = moanin::timecourse_differential_expression_analysis(
	as.matrix(data), meta, contrast)
    contrast_name = gsub(" ", "", contrast_formula, fixed=TRUE)
    contrast_name_pval = paste(contrast_name, "-pval", sep="")
    contrast_name_qval = paste(contrast_name, "-qval", sep="")
    de_analysis[contrast_name_pval] = model$pval_lrt
    de_analysis[contrast_name_qval] = model$qval_lrt
